Supplementary Information

### 2021-01-29 doc/manuscript/MEE_manuscript_SI.Rmd
remove decadal analysis appendix
don't think this is needed

#Appendices
site_details_appendix <- "S1"
DBH_reconstruction <- "S2"
climate_correction <- "S3"
traditional_comparison <- "S4"
changing_climate <- "S5"
decadal_analysis_appendix <- "S6"

site_details_appendix_title<- "Appendix S1. Site Details"
DBH_reconstruction_title <- "Appendix S2. Methods for reconstruction of $DBH$"
climate_correction_title <- "Appendix S3. Methods for climate data evaluation and correction"
traditional_comparison_title <- "Appendix S4. Methods for comparing our approach with traditional methods"
changing_climate_title <- "Appendix S5. Dealing with rapidly changing climate and tree growth"
decadal_analysis_appendix_title <- "Appendix S6. Analysis of DBH-growth relationships by decade"

@@

decadal_plot_BCNM_legend = "Figure. S32. (Decadal BCNM)"
decadal_plot_HKK_legend = "Figure. S33. (Decadal HKK)"
decadal_plot_SCBI_legend = "Figure. S34. (Decadal SCBI)"
decadal_plot_LDW_legend = "Figure. S35. (Decadal LDW)"
decadal_plot_HF_legend = "Figure. S36. (Decadal HF)"
decadal_plot_ZOF_legend = "Figure. S37. (Decadal ZOF)"
decadal_plot_NIO_legend = "Figure. S38. (Decadal NIO)"
decadal_plot_LT_legend = "Figure. S39. (Decadal LT)"
decadal_plot_CB_legend = "Figure. S40. (Decadal CB)"
decadal_plot_SC_legend = "Figure. S41. (Decadal SC)"

@@

## `r decadal_analysis_appendix_title`

**(CAMERON'S WORK [IN THIS REPO](https://github.com/EcoClimLab/tree-rings_global-change))**

>>>>

#Appendices
site_details_appendix <- "S1"
DBH_reconstruction <- "S2"
climate_correction <- "S3"
traditional_comparison <- "S4"
changing_climate <- "S5"

site_details_appendix_title<- "Appendix S1. Site Details"
DBH_reconstruction_title <- "Appendix S2. Methods for reconstruction of $DBH$"
climate_correction_title <- "Appendix S3. Methods for climate data evaluation and correction"
traditional_comparison_title <- "Appendix S4. Methods for comparing our approach with traditional methods"
changing_climate_title <- "Appendix S5. Dealing with rapidly changing climate and tree growth"

@@

decadal_plot_BCNM_legend = "Figure S32. (Decadal BCNM)"
decadal_plot_HKK_legend = "Figure S33. (Decadal HKK)"
decadal_plot_SCBI_legend = "Figure S34. (Decadal SCBI)"
decadal_plot_LDW_legend = "Figure S35. (Decadal LDW)"
decadal_plot_HF_legend = "Figure S36. (Decadal HF)"
decadal_plot_ZOF_legend = "Figure S37. (Decadal ZOF)"
decadal_plot_NIO_legend = "Figure S38. (Decadal NIO)"
decadal_plot_LT_legend = "Figure S39. (Decadal LT)"
decadal_plot_CB_legend = "Figure S40. (Decadal CB)"
decadal_plot_SC_legend = "Figure S41. (Decadal SC)"

@@
